HW3 Yu Yin BIOSTAT578
========================================================
Download the mapping information and processed data and Sanitize data and metadata

```{r eval=FALSE}
gds <- getGEO("GSE29619") 
gds_new <- gds
sanitize_pdata <- function(pd){
  keepCols <- c(
    "characteristics_ch1.1", "characteristics_ch1.2",
    "description", 
    "supplementary_file")
  pd <- pd[, keepCols]
  colnames(pd) <- c("ptid", "time", "description", "filename")
  pd$ptid <- gsub(".*: ", "", pd$ptid)
  pd$time <- gsub(".*: ", "", pd$time)
  pd$time<-gsub("Day", "D", pd$time)
  pd$description<-gsub("(-\\w*){2}$", "", pd$description)
  pd$filename<-basename(as.character(pd$filename))
  pd$filename<-gsub(".CEL.gz", "", pd$filename)
  pd
}

pData(gds_new[[1]]) <- sanitize_pdata(pData(gds_new[[1]]))
pData(gds_new[[2]]) <- sanitize_pdata(pData(gds_new[[2]]))
pData(gds_new[[3]]) <- sanitize_pdata(pData(gds_new[[3]]))

TIV_08 <- gds_new[[1]][ , grepl("2008-TIV", pData(gds_new[[1]])$description)]
LAIV_08 <- gds_new[[1]][ , grepl("2008-LAIV", pData(gds_new[[1]])$description)]
TIV_07 <- gds_new[[3]][ , grepl("2007-TIV", pData(gds_new[[3]])$description)]

```

install GEO meta database

```{r eval=FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite("GEOmetadb")
library(GEOmetadb)
library(GEOquery)
biocLite("limma")
library(limma)
```

find the design matrix:
```{r eval=FALSE}
new_set <- ExpressionSet(assayData = exprs(gds_new[[1]])+1)
TIV_08 <- new_set
pData(TIV_08) <- pData(gds_new[[1]])
mm_TIV_08 <- model.matrix(~ptid+time, TIV_08) 
```

fit the linear model:

```{r eval=FALSE}
new_set_voom <- voom(TIV_08,design = mm_TIV_08)
lm <- lmFit(new_set_voom, mm_TIV_08)
eb <- eBayes(lm)
```

choose significant subset:

```{r eval=FALSE}
library(data.table)
topT3 <- data.table(topTable(eb, coef = "timeD3", adjust = 'fdr',p.value= 0.01))
topT7 <- data.table(topTable(eb, coef = "timeD7", adjust = 'fdr',p.value=0.01))
```

make the heat plot:

```{r eval=FALSE}
library(pheatmap)
PValue <- matrix(c(topT3$logFC[topT3$adj.P.Val<0.1],topT7$logFC[topT7$adj.P.Val<0.1]),ncol=2)
rownames(PValue) <- rownames(topT3)[topT3$adj.P.Val<0.1]
colnames(PValue) <- c("timeD3","timeD7")
pheatmap(PValue)
```

part c: get the files first:

```{r eval=FALSE}
files <- list.files(path = "Data/GEO/", pattern = "GSE29619_T.*.gz", full.names = TRUE)
file_list <- lapply(files, read.table, header=TRUE)
```

We load the `GSEAbase` package for loading gene sets and convert the gene sets to gene indices

```{r eval=FALSE}
library(BiocInstaller)
biocLite("GSEABase")
library(GSEABase)
c2_set <- getGmt("GSEA-sets/c2.all.v4.0.symbols.gmt")
gene_ids <- geneIds(c2_set)
```

Camera requires gene-indices
```{r eval=FALSE}
sets_indices <- symbols2indices(gene_ids, fData(gds_new[[1]])[,"Gene Symbol"])
```

compare by timegroups

```{r eval=FALSE}
res <- vector("list",length = 2)
ct <- 1
for(i in c(3,7))
{
  contrast <- paste0("timeD",i)
  cont_matrix <- makeContrasts(contrast, levels=mm_TIV_08)
  res[[ct]] <- camera(new_set_voom, sets_indices, design=mm_TIV_08, contrast=cont_matrix, sort=FALSE)
  ct <- ct+1
}
PValue <- sapply(res, function(x){ifelse(x$Direction=="Up", -10*log10(x$PValue), 10*log10(x$PValue))})
rownames(PValue) <- rownames(res[[1]])
PValue_max <- rowMax(abs(PValue))
PValue_small <- PValue[PValue_max>30, ]
anno <- data.frame(Time=paste0("timeD",c(3,7)))
rownames(anno) <- colnames(PValue_small)  <- paste0("timeD",c(3,7))
```

make the heat plot:

```{r eval=FALSE}
pheatmap(PValue_small, cluster_cols=FALSE,show_rownames=FALSE)
```















